High geomagnetic field intensity in the late Mesoproterozoic recorded by Midcontinent Rift anorthosite xenoliths

### 2021-09-29 manuscript/Manuscript.tex

\begin{figure}
\noindent\includegraphics[width=\textwidth]{Petro_QDM.png}
\caption{\footnotesize{Thin section petrographic and magnetic images of anorthosites from Duluth Complex Anorthositic Series (left column) and anorthosite xenolith MS99033 from the Beaver River diabase (right column). Petrographic images (A-D) show Duluth Complex anorthosite have euhedral, elongate plagioclase crystals with interlocking texture and strong igneous foliation. The plagioclase can contain abundant Fe-Ti oxide needles (C) that have preferred orientations that are often parallel with the (010) planes of plagioclase. In contrast, plagioclase of the anorthosite xenolith MS99033 do not enclose oxide needles. Magnetic field maps acquired by the quantum diamond microscope (QDM) show that the oxide needles within Duluth plagioclase are strongly magnetic as evidenced through the overlapping magnetic dipole fields exerted above the oxides in (E). In comparison, the plagioclase of MS99033 is not magnetic. }}
\label{fig:Petro_QDM}
\end{figure}

@@

This proposed magmatic evolution of the Duluth Complex is in distinct contrast to the emplacement of the Beaver River diabase which rapidly ascended and entrained the anorthosite xenoliths directly into shallow chambers \cite{Flower1980a, Miller1997a, Zhang2021b}. Particularly, \citeA{Miller1997a} observed a high state of structural disorder within plagioclase of the Beaver River anorthosite using X-ray diffraction analyses. This is consistent with the interpretation that these anorthosite were rapidly transported into shallow magma chambers without reaching structural equilibrium. Within the Beaver River anorthosite xenoliths, the titanomagnetite needles and the symplectic magnetite-ilmenite intergrowths are absent (Fig. \ref{Petro_QDM}). Instead, relatively sparse titano-magnetite cinterstitial to the plagioclase are typical of Beaver River anorthosites (Fig, \ref{}).

@@

All units have Q$_{PI}$ scores \cite{Biggin2014a} ranging between 5 and 6 (Table \ref{tab:QPI}). All sites passed AGE, TRM and ALT (pTRM checks passed and high-temperature steps that looked to be suffering from alteration were excluded), ACN and MD (no significant sagging or zigzagging).

>>>>

\begin{figure}
\noindent\includegraphics[width=\textwidth]{Petro_QDM.png}
\caption{\footnotesize{Thin section petrographic and magnetic images of anorthosites from Duluth Complex Anorthositic Series (left column) and Beaver River anorthosite xenolith from which paleomagnetic site AX16 and geochronology sample MS99033 were collected (right column; \citeA{Zhang2021b}). Petrographic images (A-D) show Duluth Complex anorthosite have euhedral, elongate plagioclase crystals with interlocking texture and strong igneous foliation. The plagioclase can contain abundant Fe-Ti oxide needles (C) that have preferred orientations that are often parallel with the (010) planes of plagioclase. In contrast, plagioclase of sample MS99033 do not enclose oxide needles. Magnetic field maps acquired by the quantum diamond microscope (QDM) show that the oxide needles within Duluth plagioclase are strongly magnetic as evidenced through the overlapping magnetic dipole fields exerted above the oxides in (E). In comparison, the plagioclase of MS99033 is not magnetic. }}
\label{fig:Petro_QDM}
\end{figure}

@@

This proposed magmatic evolution of the Duluth Complex is in distinct contrast to the emplacement of the Beaver River diabase which rapidly ascended and entrained the anorthosite xenoliths directly into shallow chambers \cite{Flower1980a, Miller1997a, Zhang2021b}. Particularly, \citeA{Miller1997a} observed a high state of structural disorder within plagioclase of the Beaver River anorthosite using X-ray diffraction analyses. This is consistent with the interpretation that these anorthosite were rapidly transported into shallow magma chambers without reaching structural equilibrium. Within the Beaver River anorthosite xenoliths, the titanomagnetite needles and the symplectic magnetite-ilmenite intergrowths are absent (Fig. \ref{Petro_QDM}). Instead, relatively sparse titano-magnetite interstitial to the plagioclase are typical of Beaver River anorthosites (Fig, \ref{}).

@@
